AggregateCounts

### 2021-06-29 R/AggregateCounts.Rmd
Added figures for z-slice

slicedData<-GetSliceData()

#merge with metadata
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)

metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
sliceDataMeta <- anti_join(sliceDataMeta, remove)

sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
sliceDataMeta<-sliceDataMeta %>% mutate(Height = Zdim*Slice)
sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)

ggplot()+
  geom_point(data = sliceDataMeta,aes(x=NormBiomass,y=Height, color = Condition, shape = TimePoint ),size=2)+

  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  facet_grid(Channel~Condition)+
  theme(plot.title = element_text(hjust = 0.5))

>>>>

#Input data
#####
#get data from csv file
slicedData<-GetSliceData()
#get metadata
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)
#merge files
metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
#clean up
remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
sliceDataMeta <- anti_join(sliceDataMeta, remove)
#rename variables
sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "wt", "pqsL", "phz"),labels = c('Sa mono','wt co', 'pqsL co', 'phz co'))
sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
#calculate relative biomass
sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)

#####
#Plot Data
#####
ggplot()+
  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
#####
#Max slice?
sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint) %>% mutate(MaxHeight = max(Height))
ggplot()+
  geom_point(data = maxSlice%>% filter(MaxHeight<120 & MaxHeight>50),aes(x=Replicate,y=MaxHeight, color = Condition),size=4)+
facet_grid(.~TimePoint, scales = "free", space = "free")+
  scale_color_brewer(palette = "Set1")+
  geom_hline(yintercept = 120)+
  geom_hline(yintercept = 50)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),axis.text.x = element_text(angle = 70, hjust = 1))

ggplot()+
  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
  geom_smooth(data = sliceDataMeta %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
